### 2019-06-13 doc/chapters/towards_verifying_addition.tex
added ,
Corrected properties names

\chapter{Towards Verifying the Addition with Zero Property}
\label{chap:verify_add}

@@

This is due to the internal design of Scala.
It's possible to reason about case object but not about object.
This needs a fundamental knowledge of Scala and some functional paradigms that should not be part of this thesis.
The \href{https://github.com/epfl-lara/stainless/issues/520}{issue \mypound520} on Stainless GitHub gives some thoughts if you want to know more.

>>>>

\chapter{Towards Verifying the Addition-with-Zero Property}
\label{chap:verify_add}

@@

This is due to the internal design of Scala.
It's possible to reason about case object but not about object.
This needs a fundamental knowledge of Scala and some functional paradigms that should not be part of this thesis.
The \href{https://github.com/epfl-lara/stainless/issues/520}{issue \mypound520} on Stainless GitHub gives some thoughts, if you want to know more.
